Capturing the shape of our experiences and how we remember them

### 2018-08-20 paper/main.tex
moved additional metrics and list learning to supplemental

Then, we computed a group-averaged recall event model and video-recall event correlation matrix. For each participant (and each recall event), we sorted the recall event vectors (across all participants) according to the video event with the highest correlation. We then averaged the recall event vectors within each group. This yielded an average recall event vector for all but one (of 34) video events, since no participant remembered one of the events according to our model. Lastly, we computed an average recall event (34) by video event (34) correlation matrix, and highlighted the cell with the highest correlation value with a yellow border (Fig.~\ref{fig:model}h). Notably, this matrix displayed high correlation values along the diagonal and low correlations in the off-diagonal cells. This suggests that on average, participants were able to recapitulate the events in the episode in a specific, highly descriminable way.
% NOTE: ^ possibly need a null model for the group analysis.  I think it could be to get a result that looks like this even if we scrambled the text. My concern is that I'm grouping the recall events by the video event they were most similar to, and then averaging, which may give rise to a smooth looking plot without any real information there...

@@

\begin{figure}[t!]
\centering
\includegraphics[width=1\textwidth]{figs/3_trajectory.pdf}
\caption{\small \textbf{Video and recall trajectory plots.} A). 2-dimensional embedding of the video events model. The arrows indicate the forward direction of the video events. B). 2-dimensional embedding of the average recall events model.  The colors refer to the most similar video events. The directional lines connecting the points represent the true video event order. The arrows represent the average direction of all recall event transitions (i.e. a line segment connecting two consecutive recall event vectors) that intersected a box (width=.25) centered on the origin of the arrow.}
\label{fig:trajectory}
\end{figure}

@@

% NOTE: Not sure if this part (below) is necessary, but if it is, then I think we need to come up with a null test to say that participants fits are better than chance

% Notably, many of the participants' recall trajectories appear to recover the shape of the video stimulus. To quantify this similarity, we measured the average euclidean distance between each each segment of the video model (e.g. the line formed by successive video events) and the closest recall event for each participant.  Inuitively, if the participant approximately remembered every video event, the measure would approach 0. The more missing recall events, the higher the value. We found that this shape measure was highly correlated to the number of events remembered across participants (Pearson's $r$(16)=-.87, p$<$.001). While these measures are highly correlated (as might be expected), there are cases where the measures dissociate.  For example participant X and X recalled exactly the same number of events, but the shape measure is drastically different between them.  Conversely, participant X and X had the same shape measure, but there was a large difference in the number of events recalled. Thus, measuring similarity in shape between the video and recall models provides unique information about participant's recall behavior that is not captured by classic measures of memory accuracy.

@@

\subsubsection{Memorability by event and topics}
A noteworthy advantage of representing naturalistic stimuli/memory using this approach is that the event models can be mapped back to the language used to fit the model(s).  This allows for analysis and visualization of the language used when participant's recounted their experiences.  In this next analysis, we 1) quantified the memorability of each video event and 2) used memorability to plot the top words for the most and least memorable scenes, and also aggregated across the entire video.

@@

\subsubsection{Additional measures of naturalistic memory}
Representing the video and verbal recall as events in ``topic space'' also affords us the ability to characterize the quality of recall in a more fine-grained and nuanced way than what was previously possible. To quantify the similarity between the video model and individual recall models, we considered a number of novel metrics.  First, we tested whether each participant's recall model matched the movie model in a general sense. To do this, for each participant we filtered the video model to only include the events that the participant remembered. Then, we computed the root mean squared difference (RMSD) between the video model and the recall model. As an example, if the participant remembered all the events in order (with perfect precision), the expected distance value would be 0. However, if they remembered a subset of events, events our of order or with low precision the expected distance would be greater than 0. To assess significance, we performed a permutation test where we circularly shifted the recall model (10000 times) and recomputed the RMSD. The recall model significantly matched the video model for nine of the participants ($p$<.05; participants: 3-4, 8-13, 17 and the p-value for the rest of the participants was less than .25). Furthermore, the RMSD values were significantly correlated to hand annotated memory performance across participants (Pearson's $r$(16)=-.57, $p$=.016). Thus, a closer match between the video and recall event models was related to better recall performance.

Next, we tested whether participants who recalled more events were also more precise in their recollections. For each participant, we computed the correlation between each recall event and its matching video event (only for the events which they recalled). This resulted in a single number for each recalled event indexing how similar the recall event was to its matching movie event (i.e the ``precision'' of the recall). We then averaged the correlations within participant. In line with our prediction, there was a strong correlation between hand annotated memory performance and precision suggesting that participants who remembered more events also remembered them more veridically (Pearson's $r$(16)=.74, p=.0006). Next, we considered the distinctiveness of each recall event. That is, how uniquely a recall event matched a given video event compared to all other video events. We hypothesized that participants with high memory performance might describe each event in a more distinctive way (relative to those with lower memory performance who might describe events in a more general way). To this end, we computed a `distinctiveness' score for each participant (i.e. 1 - the correlation between a recall event and all non-matching video events).  Then, we averaged this measure over recall events within participant.  We found that participants with higher hand annotated memory performance also had higher distinctiveness scores (Pearson's $r$(16)=.8, $p$=.0001).

Just like in a traditional ``free-recall'' list-learning experiment where participants view a list of words and then verbally recall them, our video-recall matching analysis approach affords us the ability to analyze memory in the same way. The recalled events can be treated as ``items'' analogous to words recalled in a list-learning study. In our first set of analyses, we sought to characterize memory performance/dynamics by extending classic analyses originally designed for list-learning experiments to more naturalistic settings. First, we asked whether the estimated number of recall events ($k$) by participant was related to hand-annotated accuracy as published in Chen et al. (2017).  We found a strong positive correlation where subjects with a greater number of recall events also had better overall memory performance (Pearson's $r$(16)=.67, $p$=.003). Then, we considered how participants initiated the recall sequence (known in the literature as the `probability of first recall' or `PFR'). We found that participants tended to initiate their recall sequences with the first few events (Supp. Fig.~\ref{fig:list-learning}a), which is qualitatively very similar to previously published list learning experiments (REF?). Next, we considered another well-studied memory measure in the list-learning literature, the lag conditional response probability curve (or lag-CRP) ~\citep{Kaha96}. The result suggests a strong bias to transition sequentially events in the forward direction (Supp. Fig.~\ref{fig:list-learning}b). Finally, we assessed memory performance for each event in the video as a function of its serial position during encoding (Supp. Fig.~\ref{fig:list-learning}c). We found that there was substantial variability in memory for the different events (STAT). We also considered two additional across-participant measures of recall that characterize memory organization: temporal clustering and semantic clustering. We found that participants who clustered in time also recalled a greater number of events (Pearson's $r$(16)=.62, $p$=.007). Next, we assessed semantic clustering. We found that the semantic clustering score was related to memory performance across participants (Pearson's $r$(16)=.55, $p$=.02).  Thus, participants who organized their recalls with respect to the semantic information contained in the scene had better memory performance.

%NOTE: I'm not sure the brain stuff really fits in this paper.  It's cool, but seems like a distraction from the main point.  perhaps it needs it own paper with more motivation, and more extensive analyses (for example, what brain regions have temporal structure like the movie model?). I'm also having a hard time motivating it in the discussion, so maybe we should cut it.

% \subsubsection{Brain regions that mirror the correlational structure of naturalistic memories}.
% While each participant remembered roughly the same sequence of events, there were subtle idiosyncracies in the way each individual described the events. For example, the event by event similarity structure (e.g. the off-diagonal values of the recall correlation matrices) differed across individuals (Supp. Fig.~\ref{fig:corrmats}). We hypothesized that idiosyncracies in the recall dynamics across subjects might be related to the temporal structure of brain networks are representing the events during video viewing. Thus in the last analysis, we identified brain areas whose responses at the time of viewing exhibited the same (segmented) idiosyncratic dynamics that later appeared in that participants’ recalls.
%
% The amount of time/number of sentences used describing each scene differed drastically between participants and as compared to the original video \cite{ChenEtal17}. To account for these temporal non-linearities between the video and recall, we used dynamic time warping to align each participant's recall model and the movie model (DTW REF).  We used the resulting alignment path to warp the fMRI timeseries (for each voxel) as well as the recall model timeseries.  Then using a searchlight procedure (5mm), we computed the timepoint-by-timepoint neural correlation matrix within each searchlight. To measure the similarity between the neural and behavioral correlation matrices, we vectorized and then correlated them. The result was a correlation value for each voxel representing the extent to which the brain data mirrored the recall data.  Finally, to test the significance of the correlation values, we phase shifted the recall models (100 permuations) and recomputed the correlation values. Significance was determined by ``real'' correlation values that exceeded the 95th percentile of this null distribution. The resulting map suggests that the correlational structure of a network of brain regions including the ventromedial prefrontal cortex, anterior cingulate, and right medial temporal lobe mirror the idiosyncratic structure of participants'' recalls.
%
% \begin{figure}[t!]
% \centering
% \includegraphics[width=1\textwidth]{figs/6_brains.pdf}
% \caption{\small \textbf{Recall model correlational structure searchlight analysis.} A). We used dynamic time warping to separately align each participant's recall model to the video model. The left matrix is S13's video-recall correlation matrix before warping. The yellow stars represent the path recovered by dynamic time warping. The right matrix is the result after warping. The same warping path was applied to the fMRI timeseries (separately for each participant). Below the matrices are toy examples representing a vectorized (aligned) recall correlation matrix and a vectorized (aligned) fMRI searchlight correlation matrix. These vectors were correlated for each searchlight sphere in the brain to assess brain regions whose temporal correlation structure mirrored the participant's recall model correlation structure. B) A surface plot of brain regions whose activity patterns mirrored the participant-specific recall correlation matrix. Significance threshold (p$<$.05) derived from a permutation procedure by phase shifting the video model and recomputing the z-scores.}
% \label{fig:brainz}
% \end{figure}

\section{Discussion}
\label{sec:discussion}

Studying episodic memory is commonly distilled down to a process of matching specific moments of a past experience with specific mnemonic outcomes.  In traditional trial-based free recall and item recognition experiments, individual stimuli encountered during encoding are typically labeled as ``remembered'' or ``forgotten'' depending on whether the stimulus is recalled/recognized during a subsequent test. While this approach has advanced our understanding of human memory immensely, it does not translate well to naturalistic experiences. For one thing, the contents of our recall at any given moment might be reflected in many prior experiences/moments. Furthermore, the particular words used to describe the experience will inevitably vary across people and even across repeated recollections within an individual. Thus, there is not a ``one-to-one'' mapping between naturalistic experiences and their mnemonic counterparts. Our topic modeling approach, whereby we consider the broad ``theme'' present in different moments of participants' experiences and their memories for those experiences, affords us the ability to flexibly and accurately characterize memory for naturalistic experiences. This approach allows us to quantify which moments from the past and the current recounted experience match in terms of their thematic content and critically, our ability to perform this matching does not require participants to use any specific overlapping words.

@@

% Prior work on neural responses during naturalistic experience and recall (e.g. Hasson group) has largely focused on identifying brain regions whose responses are reliably similar across individuals. This allows one to identify which regions might be processing or representing the stimulus, or retrieving details of the experience during recall. Our approach is fundamentally different. We ask: which brain regions during movie viewing match how individual participants will recall the movie later (in terms of the temporal correlations of their recall topic trajectory)? This approach highlights regions such as the vmPFC that may respond in idiosyncratic ways across individuals, but that nonetheless play an important role in encoding experience into memory.

@@

Our metric for choosing the `best fitting' HMM was to choose the model with the $k$ value that maximized the ratio of the average `within-event' correlation values (i.e. the correlation values for blocks of consecutive timepoints the model identified as one event) and the average `across-event' correlation (i.e. the rest of the correlation values). Additionally, we included a penalty parameter that was proportional to the smoothing of the model that preferred models with smaller $k$ values. We chose $k$ values separately for the video model and for each recall model.  Then, using the best $k$ values, We fit a separate HMM for each topic model. Finally, we averaged over timepoints identified to be in the same event resulting in a events by topics matrix for the video model and each of the recall models.
%
\subsubsection{Matching recall events to video events}
To figure out which video event each recall event referred to, we correlated the video events model and each recall events model. This resulted in a video events (34) by recall events (8-27) correlation matrix (for each participant) which contains the similarity between each video event and each recall event.  To find the most likely video event that a given recall event referred to, we computed the argmax over the columns of this matrix.  The result was a list of video event indices for each participant. These indices are analogous to the values found in a ``recall matrix'' from a free recall list learning experiment, but represent the recall of particular events (instead of words, for example).
%
\subsubsection{Characterizing memory performance using traditional approaches}

\textbf{Overall Accuracy.}  To get an overall measure of the quantity of information recalled, we computed the proportion of sucessfully recalled events by counting the number of unique recall events identified by the HMM model and dividing by the total number of video events.  We performed this analysis for each participant separately.

@@

\subsubsection{Visualizing the video and recall event models}

To better understand the temporal structure of the video event model (34 events by 100 topics) and the recall event models (8-27 events by 100 topics), we used a technique called UMAP to reduce the ``topic-space'' from 100 dimensions down to 2 dimensions (REF). UMAP is a nonlinear dimensionality reduction technique which models the manifold of the data with a fuzzy topological structure, and then searches for a (2D) projection of the data that has the closest equivalent fuzzy topological structure. We concatenated (vertically stacked) all event models (video, average recall, and individual recall), and then fit and transformed all of the models at once. This assured that the models were projected into the same space.

 % \subsection{fMRI analyses}
 % Seventeen participants watched the first 50 minutes of Episode 1 of BBC's Sherlock. The video was split into two parts of approximately equal length (946 and 1030 TRs). All data were preprocessed and transformed to 3mm MNI space as described in the paper. Data were zscored across time at every voxel. 6mm smoothing was applied.
 % Files are cropped so that all video-viewing data are aligned across participants, and all recall data are aligned to the scene timestamps below. The cropping includes a constant 3-TR (4.5 sec) shift to correct for hemodynamic lag.
 %
 % \subsubsection{Searchlight analysis}
 % Our multivariate analyses were designed to capture brain regions whose timepoint-by-timepoint correlational structure mirrors the correlational structure of the participant-specific recall topic models during video viewing. To correct for non-linearities between the viewing time and recall time, for each participant we used DTW to temporally align the matrices. The algorithm recovers a path of coordinates that would bring the video and recall model in maximal temporal alignment. We used this path to warp the fMRI data and the recall model into temporal alignment (separately for each participant). Then, we conducted a searchlight analysis (5x5x5 voxel cube) where for each cube, we correlated the model timepoint-by-timepoint correlation matrix with the neural correlation matrix. To aggregate across participants, we Fisher's z-transformed the correlations and then averaged.  To assess significance, we recomputed this group analysis 100 times, but randomly phase shifted the model (by \# of timepoints - 1) by the same amount for each participant but different amounts for each permutation to build a null distribution of correlation values. Finally, we thresholded the group averaged correlation maps where the `real' correlation value for a given voxel exceeded the 95th percentile of the null distribution.

>>>>

Then, we computed a group-averaged recall event model and video-recall event correlation matrix. For each participant (and each recall event), we sorted the recall event vectors (across all participants) according to the video event with the highest correlation. We then averaged the recall event vectors within each group. This yielded an average recall event vector for all but one (of 34) video events, since no participant remembered one of the events according to our model. Lastly, we computed an average recall event (34) by video event (34) correlation matrix, and highlighted the cell with the highest correlation value with a yellow border (Fig.~\ref{fig:model}h). Notably, this matrix displayed high correlation values along the diagonal and low correlations in the off-diagonal cells. This suggests that on average, participants were able to recapitulate the events in the episode in a specific, highly descriminable way.

@@

\begin{figure}[t!]
\centering
\includegraphics[width=1\textwidth]{figs/3_trajectory.pdf}
\caption{\small \textbf{Video and recall trajectory plots.} A). 2-dimensional embedding of the video events model. The arrows indicate the forward direction of the video events. B). 2-dimensional embedding of the average recall events model.  The colors refer to the most similar video events. The directional lines connecting the points represent the true video event order. The arrows represent the group-average direction of all recall event transitions (i.e. a line segment connecting two consecutive recall event vectors) that intersected a box (width=.25) centered on the origin of the arrow.}
\label{fig:trajectory}
\end{figure}

@@

\subsubsection{Additional measures of naturalistic recall}
Representing the video and verbal recall as events in ``topic space'' also affords us the ability to characterize the quality of recall in a more fine-grained and nuanced way than what was previously possible. In addition to the shape analyses described above, we quantified the distance between each video event and its matching recall event (``precision''), the the distance between a video event and all non-matching recall events (``distinctiveness'') and the temporal order of the recall events (``order''). All three of these metrics were correlated to hand-annotated memory performance across participants ($p$<.05, see Supplemental Materials Section 1 for details).

Just like in a traditional ``free-recall'' list-learning experiment where participants view a list of words and then verbally recall them, our video-recall matching analysis approach affords us the ability to analyze memory in the same way. We considered 6 classic list-learning analyses: overall accuracy, probability of first recall, lag-conditional response probability, serial position curve, temporal clustering and semantic clustering. Extending these classic list-learning analyses to naturalistic stimuli allows to directly compare trial- and naturalistic-based recall studies (see Supplemental Materials Section 2 for details).

@@

\subsubsection{Memorability by event and topics}
A notable advantage of representing naturalistic stimuli/memory using this approach is that the event models can be mapped back to the language used to fit the model(s).  This allows for analysis and visualization of the language used when participant's recounted their experiences.  In this next analysis, we 1) quantified the memorability of each video event and 2) used memorability to plot the top words for the most and least memorable scenes, and also aggregated across the entire video.

@@

\section{Discussion}
\label{sec:discussion}
Studying episodic memory is commonly distilled down to a process of matching specific moments of a past experience with specific mnemonic outcomes.  In traditional trial-based free recall and item recognition experiments, individual stimuli encountered during encoding are typically labeled as ``remembered'' or ``forgotten'' depending on whether the stimulus is recalled/recognized during a subsequent test. While this approach has advanced our understanding of human memory immensely, it does not translate well to naturalistic experiences. For one thing, the contents of our recall at any given moment might be reflected in many prior experiences/moments. Furthermore, the particular words used to describe the experience will inevitably vary across people and even across repeated recollections within an individual. Thus, there is not a ``one-to-one'' mapping between naturalistic experiences and their mnemonic counterparts. Our topic modeling approach, whereby we consider the broad ``theme'' present in different moments of participants' experiences and their memories for those experiences, affords us the ability to flexibly and accurately characterize memory for naturalistic experiences. This approach allows us to quantify which moments from the past and the current recounted experience match in terms of their thematic content and critically, our ability to perform this matching does not require participants to use any specific overlapping words.

@@

@@

Our metric for choosing the `best fitting' HMM was to choose the model with the $k$ value that maximized the ratio of the average `within-event' correlation values (i.e. the correlation values for blocks of consecutive timepoints the model identified as one event) and the average `across-event' correlation (i.e. the rest of the correlation values). Additionally, we included a penalty parameter that was proportional to the smoothing of the model that preferred models with smaller $k$ values. We chose $k$ values separately for the video model and for each recall model.  Then, using the best $k$ values, We fit a separate HMM for each topic model. Finally, we averaged over timepoints identified to be in the same event resulting in a events by topics matrix for the video model and each of the recall models.
%
\subsubsection{Matching recall events to video events}
To figure out which video event each recall event referred to, we correlated the video events model and each recall events model. This resulted in a video events (34) by recall events (8-27) correlation matrix (for each participant) which contains the similarity between each video event and each recall event.  To find the most likely video event that a given recall event referred to, we computed the argmax over the columns of this matrix.  The result was a list of video event indices for each participant. These indices are analogous to the values found in a ``recall matrix'' from a free recall list learning experiment, but represent the recall of particular events (instead of words, for example).

\subsubsection{Visualizing the video and recall event models}
To better understand the temporal structure of the video event model (34 events by 100 topics) and the recall event models (8-27 events by 100 topics), we used a technique called UMAP to reduce the ``topic-space'' from 100 dimensions down to 2 dimensions (REF). UMAP is a nonlinear dimensionality reduction technique which models the manifold of the data with a fuzzy topological structure, and then searches for a (2D) projection of the data that has the closest equivalent fuzzy topological structure. We concatenated (vertically stacked) all event models (video, average recall, and individual recall), and then fit and transformed all of the models at once. This assured that the models were projected into the same space.

% SUPPLEMENTAL MATERIALS

\pagebreak
\begin{center}
\textbf{\large Supplemental Materials: Capturing the shape of naturalistic experiences and how we remember them}
\end{center}
\setcounter{equation}{0}
\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{page}{1}
\setcounter{section}{0}
\makeatletter
\renewcommand{\theequation}{S\arabic{equation}}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\bibnumfmt}[1]{[S#1]}
\renewcommand{\citenumfont}[1]{S#1}

\section{Additional measures of naturalistic memory}
To quantify the similarity between the video model and individual recall models, we considered a number of novel metrics.  First, we tested whether each participant's recall model matched the movie model in a general sense. To do this, for each participant we filtered the video model to only include the events that the participant remembered and computed the root mean squared difference (RMSD) between the video model and the recall model. As an example, if the participant remembered all the events in order (with perfect precision), the expected distance value would be 0. However, if they remembered a subset of events, events our of order or with low precision the expected distance would be greater than 0. To assess significance, we performed a permutation test where we circularly shifted the recall model (10000 times) and recomputed the RMSD. The recall model significantly matched the video model for nine of the participants ($p$<.05, permutation test, see Methods for details; participants: 3-4, 8-13, 17 and the p-value for the rest of the participants was less than .25). Furthermore, the RMSD values were significantly correlated to hand annotated memory performance across participants (Pearson's $r$(16)=-.57, $p$=.016). Thus, a closer match between the video and recall event models was related to better recall performance.

Next, we tested whether participants who recalled more events were also more precise in their recollections. For each participant, we computed the correlation between each recall event and its matching video event (only for the events which they recalled). This resulted in a single number for each recalled event indexing how similar the recall event was to its matching movie event (i.e the ``precision'' of the recall). We then averaged the correlations within participant. In line with our prediction, there was a strong correlation between hand annotated memory performance and precision suggesting that participants who remembered more events also remembered them more veridically (Pearson's $r$(16)=.74, $p$=.0006). Then, we considered the distinctiveness of each recall event. That is, how uniquely a recall event matched a given video event compared to all other video events. We hypothesized that participants with high memory performance might describe each event in a more distinctive way (relative to those with lower memory performance who might describe events in a more general way). To this end, we computed a `distinctiveness' score for each participant (i.e. 1 - the correlation between a recall event and all non-matching video events).  Then, we averaged this measure over recall events within participant.  We found that participants with higher hand annotated memory performance also had higher distinctiveness scores (Pearson's $r$(16)=.8, $p$=.0001).

\section{Naturalistic extensions of classic list-learning analyses}
Just like in a traditional ``free-recall'' list-learning experiment where participants view a list of words and then verbally recall them, our video-recall matching analysis approach affords us the ability to analyze memory in the same way. The recalled events can be treated as ``items'' analogous to words recalled in a list-learning study. In our first set of analyses, we sought to characterize memory performance/dynamics by extending classic analyses originally designed for list-learning experiments to more naturalistic settings. First, we asked whether the estimated number of recall events ($k$) by participant was related to hand-annotated accuracy as published in Chen et al. (2017).  We found a strong positive correlation where subjects with a greater number of recall events also had better overall memory performance (Pearson's $r$(16)=.67, $p$=.003). Then, we considered how participants initiated the recall sequence (known in the literature as the `probability of first recall' or `PFR'). We found that participants tended to initiate their recall sequences with the first few events (Supp. Fig.~\ref{fig:list-learning}a), which is qualitatively very similar to previously published list learning experiments (REF?). Next, we considered another well-studied memory measure in the list-learning literature, the lag conditional response probability curve (or lag-CRP) ~\citep{Kaha96}. The result suggests a strong bias to transition sequentially events in the forward direction (Supp. Fig.~\ref{fig:list-learning}b). Finally, we assessed memory performance for each event in the video as a function of its serial position during encoding (Supp. Fig.~\ref{fig:list-learning}c). We found that there was substantial variability in memory for the different events (STAT). We also considered two additional across-participant measures of recall that characterize memory organization: temporal clustering and semantic clustering. We found that participants who clustered in time also recalled a greater number of events (Pearson's $r$(16)=.62, $p$=.007). Next, we assessed semantic clustering. We found that the semantic clustering score was related to memory performance across participants (Pearson's $r$(16)=.55, $p$=.02).  Thus, participants who organized their recalls with respect to the semantic information contained in the scene had better memory performance.

\section{Supplemental Methods}

\subsection{Characterizing memory performance using traditional approaches}
\textbf{Overall Accuracy.}  To get an overall measure of the quantity of information recalled, we computed the proportion of sucessfully recalled events by counting the number of unique recall events identified by the HMM model and dividing by the total number of video events.  We performed this analysis for each participant separately.

@@
